---
title: "Cleaning Tweets CSV"
Author: "Ean Johnson"
output: html_notebook
---

## Import Libraries
```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
library(data.table)

```

## Remove Scietific Notation & Set character encoding
```{r}
options(scipen = 999)
```

## Import Data
```{r}
raw_tweets <- read.csv(here::here("data", "Tweets-1.csv"), header = TRUE, stringsAsFactors = FALSE) %>% janitor::clean_names()


fread(here::here("data", "Tweets-1.csv"))

str(raw_tweets)

raw_tweets$text[1:10]

```
## Cleaning to-do 
1.tweet_id - Check tweet_id for duplicates - ensure each value is unique

2. airline_sentiment - Check all possible values of airline_senitment to ensure consistency

3. negative_reason - What kind of formatting are we looking for in negative reason. - Will this be used in analysis/What formatting is needed?

5. General question - How are we going to deal with missing values? What percentage of values are missing for each column? 

6. Text - need to remove "@VirginAmerica", special characters need to be removed/edited. 

7. Text - Stemming? Lemmatization? 

8. tweet_coord - Will this be used? If so what format? Break into two columns? 

9. tweet_created - Change to date type 


## Checking tweet id 
```{r}
raw_tweets %>%
  group_by(tweet_id) %>%
  tally()

```
Only 3 different values for tweet_id. Need to create unique_id for each tweet. 

## Check airline sentiment
```{r}

raw_tweets %>%
  group_by(airline_sentiment) %>%
  tally()

```
Seems good, if we want to use

## Check airline_sentiment_confidence
```{r}
summary(raw_tweets$airline_sentiment_confidence)
```
## Check negativereason_confidence
```{r}
summary(raw_tweets$negativereason_confidence)
```
4118 NA's is a lot - Probably can't just remove all these values if we want to use. Might need to substitute average or something along those lines. 



## Check airlinesentiment_gold
Sidenote - what is this? 
```{r}
raw_tweets %>%
  group_by(airline_sentiment_gold) %>%
  tally()
```
Only 40 values, probably not useful 

## negativereason_gold
```{r}
raw_tweets %>%
  group_by(negativereason_gold) %>%
  tally()

```
Not many values here. Can we use these? Need to remove "\n" if so.


## retweet_count 
```{r}
raw_tweets %>%
  ggplot(aes(retweet_count)) +
  geom_histogram()
```
Mostly 0's 

## Cleaning text 
```{r}


```
Change to UTF-8 - Usually standard for internet text 



